The Fremont Frontier

### 2023-06-19 R/analysis.qmd
increase figure resolution and convert to jpg

---
title: "Supplement: Fremont Models"
date: "`r Sys.Date()`"
format:
  html: 
    embed-resources: true
    fig-align: center
    fig-dpi: 300
    fig-responsive: true
    number-sections: true
    number-depth: 3
    toc: true
    toc-depth: 3
    smooth-scroll: true
    theme: cosmo
    highlight-style: a11y
execute: 
  eval: true
  echo: true
  warning: false
  error: false
---

@@

library(GGally)
library(ggeffects)
library(gratia)
library(gt)
library(here)
library(mgcv)
library(patchwork)
library(sf)
library(sfdep)
library(tidyverse)
library(viridis)

@@

ggsave(
  plot = for_print,
  filename = here("figures", "covariates.png"),
  width = 7,
  height = 7 * (dy/dx),
  dpi = 300
)

@@

ggsave(
  plot = threshold_dists,
  filename = here("figures", "threshold_distributions.png"),
  width = 7,
  height = 7 * (dy/(2*dx)),
  dpi = 300
)

@@

# ggsave(
#   plot = (obs + threshold_map),
#   filename = here("figures", "threshold_map.png"),
#   width = 7,
#   height = 7 * (dy/(2*dx)),
#   dpi = 300
# )

@@

```{r}
#| out-width: "80%"
#| fig-align: center

@@

appraise(fremont)

draw(fremont, residuals = TRUE)

@@

appraise(fremont$gam)

draw(fremont$gam)

@@

appraise(fremont$gam)

draw(parametric_effects(fremont$gam))

draw(fremont$gam)

@@

margins <- ggpredict(fremont) |>
  unclass() |>
  bind_rows() |>
  filter(group != "area") |>
  rename(
    "y" = predicted,
    "ymin" = conf.low,
    "ymax" = conf.high,
    "variable" = group
  ) |> 
  mutate(
    # hacky way to "clip" the ribbon before expanding in ggplot
    ymax = ifelse(ymax > 100, 100, ymax)
  )

@@

marginal_response <- ggplot(margins, aes(x, y)) +
  geom_ribbon(
    aes(ymin = ymin, ymax = ymax, fill = variable)
  ) + 
  scale_fill_manual(
    values = c("#4F3824", "#D1603D", "#DDB967", "#848FA5")
  ) +
  geom_line(
    linewidth = 2,
    color = alpha('white', 0.5),
    lineend = "round"
  ) +
  geom_line(
    linewidth = 1,
    lineend = "round"
  ) +
  geom_label(
    data = response_labels,
    aes(x, y, label = label),
    size = 4,
    hjust = response_labels$hjust,
    vjust = 1,
    label.size = NA,
    alpha = 0.5,
    lineheight = 0.88
  ) +
  labs(
    x = NULL,
    y = "Number of sites"
  ) +
  facet_wrap(
    ~variable, 
    scale = "free_x"
  ) +
  scale_x_continuous(breaks = scale_pretty) +
  coord_cartesian(ylim = c(0, 100)) +
  theme_bw(12) +
  theme(
    axis.title.y = element_text(size = 13),
    legend.position = "none",
    panel.grid = element_blank(),
    strip.background = element_blank(),
    strip.text = element_blank()
  )

ggsave(
  plot = marginal_response,
  filename = here("figures", "marginal_response.png"),
  width = 5,
  height = 5 * 0.93,
  dpi = 300
)

@@

ggsave(
  plot = (obs + estimate),
  filename = here("figures", "model-map.png"),
  width = 7,
  height = 7 * (dy/(2*dx)),
  dpi = 300
)

ggsave(
  plot = (estimate + threshold_map),
  filename = here("figures", "threshold_map.png"),
  width = 7,
  height = 7 * (dy/(2*dx)),
  dpi = 300
)

>>>>

---
title: "Supplement: Fremont Models"
date: today
format:
  html: 
    embed-resources: true
    fig-align: center
    fig-dpi: 300
    fig-responsive: true
    number-sections: true
    number-depth: 3
    toc: true
    toc-depth: 3
    smooth-scroll: true
    theme: cosmo
    highlight-style: a11y
execute: 
  eval: true
  echo: true
  warning: false
  error: false
---

@@

library(GGally)
library(ggeffects)
library(gt)
library(here)
library(mgcv)
library(patchwork)
library(sf)
library(sfdep)
library(tidyverse)
library(viridis)

@@

ggsave(
  plot = for_print,
  filename = here("figures", "covariates.jpg"),
  width = 5.75,
  height = 5.75 * (dy/dx),
  dpi = 600
)

@@

ggsave(
  plot = threshold_dists,
  filename = here("figures", "threshold_distributions.jpg"),
  width = 5.75,
  height = 5.75 * (dy/(2*dx)),
  dpi = 600
)

@@

@@

@@

@@

@@

@@

margins <- ggpredict(fremont) |>
  unclass() |>
  bind_rows() |>
  as_tibble() |> # the "ggeffects" class doesn't want to let go
  filter(group != "area") |>
  rename(
    "y" = predicted,
    "ymin" = conf.low,
    "ymax" = conf.high,
    "variable" = group
  ) |> 
  mutate(
    # hacky way to "clip" the ribbon before expanding in ggplot
    ymax = ifelse(ymax > 100, 100, ymax)
  )

@@

marginal_response <- ggplot(margins, aes(x, y)) +
  geom_ribbon(
    aes(ymin = ymin, ymax = ymax, fill = variable)
  ) + 
  scale_fill_manual(
    values = c("#4F3824", "#D1603D", "#DDB967", "#848FA5")
  ) +
  geom_line(
    linewidth = 2,
    color = alpha('white', 0.75),
    lineend = "round"
  ) +
  geom_line(
    linewidth = 1,
    lineend = "round"
  ) +
  geom_label(
    data = response_labels,
    aes(x, y, label = label),
    size = 4,
    hjust = response_labels$hjust,
    vjust = 1,
    label.size = NA,
    alpha = 0.5,
    lineheight = 0.88
  ) +
  labs(
    x = NULL,
    y = "Number of sites"
  ) +
  facet_wrap(
    ~variable, 
    scale = "free_x"
  ) +
  scale_x_continuous(breaks = scale_pretty) +
  coord_cartesian(ylim = c(0, 100)) +
  theme_bw(12) +
  theme(
    axis.title.y = element_text(size = 13),
    legend.position = "none",
    panel.grid = element_blank(),
    strip.background = element_blank(),
    strip.text = element_blank()
  )

ggsave(
  plot = marginal_response,
  filename = here("figures", "marginal_response.jpg"),
  width = 5,
  height = 5 * 0.93,
  dpi = 600
)

@@

ggsave(
  plot = (obs + estimate),
  filename = here("figures", "model-map.jpg"),
  width = 5.75,
  height = 5.75 * (dy/(2*dx)),
  dpi = 600
)

ggsave(
  plot = (estimate + threshold_map),
  filename = here("figures", "threshold_map.jpg"),
  width = 5.75,
  height = 5.75 * (dy/(2*dx)),
  dpi = 600
)

### 2023-06-19 manuscript/manuscript.qmd
increase figure resolution and convert to jpg

---
title: The Fremont Frontier
subtitle: Living at the Margins of Maize Farming
date: today
author:
  - name: Kenneth B. Vernon
    email: Kenneth.Vernon@colorado.edu
    affiliations: 
      - id: colorado
        address: | 
          Center for Collaborative Synthesis in Archaeology,  
          Institute of Behavioral Science,  
          University of Colorado, Boulder,  
          1440 15th Street,  
          Boulder, CO 80302
    attributes:
        corresponding: true 
  - name: Peter M. Yaworsky
    affiliations:
      - id: aarhus-culture
        address: |
          Department of Culture and Heritage Studies, 
          School of Culture and Society, 
          Aarhus University, 
          Moesgård Allé 20, building 4216, 
          8270 Højbjerg, Denmark   
      - id: aarhus-biodiversity
        address: |
          Center for Biodiversity Dynamics in a Changing World, 
          Department of Biology, 
          Aarhus University, 
          Ny Munkegade 114-116, 
          8000 Aarhus C, Denmark
  - name: Weston McCool
    affiliations:
      - id: utah-anthropology
        address: | 
          University of Utah Department of Anthropology, 
          260 S. Central Campus Drive, RM 4625, 
          Salt Lake City, UT 84112
  - name: Jerry D. Spangler
    affiliations:
      - ref: utah-anthropology
  - name: Simon Brewer
    affiliations:
      - id: utah-geography
        address: |
          University of Utah Department of Geography, 
          260 S. Central Campus Drive, RM 4625, 
          Salt Lake City, UT 84112
      - id: gcsc
        address: |
          University of Utah Global Change and Sustainability Center, 
          115 South 1460 East, RM 234 FASB, 
          Salt Lake City, UT 84112
  - name: Brian F. Codding
    affiliations:
      - ref: utah-anthropology
      - ref: gcsc
abstract: |
  The Fremont provide an important case study to examine the resilience of ancient farmers to climatic downturns, for they lived at the far northern margin of intensive maize agriculture in the American West, where the constraints on maize production are made abundantly clear. Using a tree-ring and simulation-based reconstruction of average annual precipitation and maize growing degree days, along with cost-distance to perennial streams, we model spatial variability in Fremont site density in the eastern Great Basin. The results of our analysis have implications for defining the ecological envelope in which farming is a viable strategy across this arid region and can be used to predict where and why maize farming strategies might evolve and eventually collapse as climate changes over time.
keywords:
  - Ideal Free Distribution
  - Great Basin
  - Paleoclimate Reconstruction
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Quaternary International
      formatting: preprint
      model: 3p
execute: 
  echo: false
  error: false
  warning: false
---

@@

![
On the left is an overview map showing the project area with modern satellite imagery. Dark green colors represent high elevation, high precipitation areas. The large beige area in the northwest is the Bonneville Basin. What remains of the Great Salt Lake can be seen just west of Salt Lake City. For visualization purposes, the map on the right shows the relative density of archaeological sites (see the section on site data below for details on how we calculate relative density). Please note that although the map appears to show many empty watersheds, most do in fact contain archaeological sites, just at extremely low densities.
](../figures/overview.png){#fig-overview fig-align="center" width="6in"}

@@

![
Linear responses of average water-year precipitation (mm), average growing-season maize gdd (C), and cost-distance to streams (hours) to changes in elevation (m). See methods for how these values were calculated and results for more details.
](../figures/elevation-everything.png){#fig-elevation fig-align="center" width="4in"}

@@

Many social and ecological variables may be relevant to defining a general measure of $S_i$, but here we are focusing on ecological determinants of intrinsic habitat quality, $Q_i$, that are specific to maize farmers. Our reasoning here is fairly straightforward. If we assume that the distribution of Fremont populations across habitats is at equilibrium, then we can combine this concept of maize-specific suitability with the input matching rule to reconstruct the ranking of habitats on the basis of ecologically-relevant parameters. That is, it follows from their being at equilibrium that any observed differences in population size must be the result of differences in $Q_i$, that $Q_i \approx f(N_i)$ at equilibrium. So, if we have some proxy for $N_i$, like the distribution of Fremont sites across habitats, we can model that value as a function of ecological covariates $X_i$, then use the resulting model to reconstruct $Q_i \approx f(X_i)$, giving us the maize niche for Fremont farmers, both in geographic and ecological space.

@@

@fig-overview shows the relative density of Fremont sites across watersheds. The *relative* density refers to the density of feature-weighted sites ($D_i = N_i/area_i$) divided by the maximum density ($max\;D$) across all watersheds, thus scaling the density estimates to the unit interval [0,1]. Using the relative density is just a way of avoiding any implication that we have an independent estimate of the absolute number of Fremont sites in the area, and not just an estimate based on a thinned sample.

@@

![
Distribution of covariates across watersheds. These include maize growing degree days (GDD), annual precipitation (precipitation), and cost-distance to streams (Streams).
](../figures/covariates.png){#fig-covariates fig-align="center" width="6in"}

@@

The response variable is a count $N$ of sites per watershed $i$, so it should arise as the result of a Poisson process. Given the trade-offs outlined above, we also expect it to exhibit a non-linear response to precipitation, GDD, and cost-distance to streams, so we fit a generalized additive model (GAM) with a log-link to the data using the R package mgcv [@wood2004]. Although we expect the outcome to be Poisson distributed, we use a negative binomial distribution here, as this includes a parameter, $r$, that can account for potential dispersion without giving up the inferential benefits of maximum likelihood.

$$
\begin{aligned}
N_i \sim& \;NB\,(\lambda, r)\\
E\,(N_i) =& \;\lambda_i\\
log\, (\lambda_i) =& \;log\, (area_i) + s(precipitation_i) + streams_i + gdd_i + protected_i
\end{aligned}
$$

@@

![
Marginal response plots. Each plot shows the response of site counts to changes in a target covariate while holding all other variables at their mean.
](../figures/marginal_response.png){#fig-responses fig-align="center" width="5in"}

@@

Our results indicate that Fremont maize farmers generally preferred warmer watersheds with longer growing seasons, moderate levels of precipitation (in the range of 400-600 mm), and greater access to perennial streams, as shown by the marginal response plots in Fig. 3. While site counts exhibit a positive linear response to maize GDD, for maize has an upper threshold temperature at which point it no longer grows. Plus, increased temperatures trade-off with water availability, with warmer conditions being better for plant growth but at the same time increasing water demand on the plant to keep up with growth [@ramankutty2002]. The linear relationship between site counts and maize GDD is, thus, relative to the observed distribution of that variable within the study area and should not be used to generalize to a larger geographic extent.

@@

Provided that the trade-off between precipitation and temperature is driven largely by elevation in this region, it would seem likely that the western Fremont chose site locations at elevations that maximized agricultural suitability, as evidenced by the estimated distribution of sites across watersheds (see Fig. 4), though we caution that watersheds are coarse grained units of analysis. Given the topography of the study area, this trade-off would also suggest that areas suitable for maize agriculture take the form of a thin band around the lower slopes of mountain ranges (or lower canyons in the Uintas). Such a band would be akin to a Goldilocks zone for maize agriculture (Yaworsky et al, this issue), a place where the optima for GDD and precipitation overlap, though we should not make too much of this idea, for it is an area of overlap for continuous ecological gradients, not a region demarcated by anything like a perfect line. It also must be emphasized that what matters most for maize agriculture is not necessarily where precipitation falls, but where it accumulates once it enters the streamflow network. Of course, that will largely be a function of elevation in this region, or changes in elevation, so it will still be in proximity to the Goldilocks zone, though perhaps not perfectly coincident with it. At any rate, given these considerations, it would perhaps be more accurate to characterize the trade-off confronting the Fremont as one between what we might call water availability (including general precipitation across the streamflow network, water runoff, proximity to perennial surficial sources, and irrigation potential, among other things) and temperature (including, but not limited to, the length of the growing season and the number of frost-free days).

@@

![
The map on the left shows the relative density of feature-weighted site counts as estimated by the model, with lighter colors representing larger relative densities, darker colors representing smaller relative densities. The map on the right shows which watersheds are in the rain-fed maize farming niche for at least half of the Fremont sequence. The light green color indicates those that are in the niche.
](../figures/threshold_map.png){#fig-thresholds fig-align="center" width="6in"}

@@

But setting aside those methodological issues, some much more interesting explanations may be offered, at least from the perspective of theory. In particular, the spatial covariance structure in our model may be picking up on the structure of the streamflow network, specifically the accumulation of water run-off as a function of slope. This would suggest that if there are more people in one watershed, there should be more more people in the downstream watershed, too, at least relative to other watersheds with similar precipitation and GDD values. In the language of the IFD model, the suitability of the watershed habitat should propagate through the streamflow network. Exploring that intuition in a more systematic way, however, would require much more careful consideration of streamflow. Unfortunately, that is well beyond the scope of the current paper.

@@

![
Geographic distribution of Fremont sites across watersheds. The left panel shows the relative density derived from observed site counts, and the right panel shows the relative density from the estimated site counts.
](../figures/model-map.png){#fig-model-map fig-align="center" width="6in"}

>>>>

---
title: The Fremont Frontier
subtitle: Living at the Margins of Maize Farming
date: today
author:
  - name: Kenneth B. Vernon
    email: Kenneth.Vernon@colorado.edu
    affiliations: 
      - id: colorado
        address: | 
          Center for Collaborative Synthesis in Archaeology,  
          Institute of Behavioral Science,  
          University of Colorado, Boulder,  
          1440 15th Street,  
          Boulder, CO 80302
    attributes:
        corresponding: true 
  - name: Peter M. Yaworsky
    affiliations:
      - id: aarhus-culture
        address: |
          Department of Culture and Heritage Studies, 
          School of Culture and Society, 
          Aarhus University, 
          Moesgård Allé 20, building 4216, 
          8270 Højbjerg, Denmark   
      - id: aarhus-biodiversity
        address: |
          Center for Biodiversity Dynamics in a Changing World, 
          Department of Biology, 
          Aarhus University, 
          Ny Munkegade 114-116, 
          8000 Aarhus C, Denmark
  - name: Weston McCool
    affiliations:
      - id: utah-anthropology
        address: | 
          University of Utah Department of Anthropology, 
          260 S. Central Campus Drive, RM 4625, 
          Salt Lake City, UT 84112
  - name: Jerry D. Spangler
    affiliations:
      - ref: utah-anthropology
  - name: Simon Brewer
    affiliations:
      - id: utah-geography
        address: |
          University of Utah Department of Geography, 
          260 S. Central Campus Drive, RM 4625, 
          Salt Lake City, UT 84112
      - id: gcsc
        address: |
          University of Utah Global Change and Sustainability Center, 
          115 South 1460 East, RM 234 FASB, 
          Salt Lake City, UT 84112
  - name: Brian F. Codding
    affiliations:
      - ref: utah-anthropology
      - ref: gcsc
abstract: |
  The Fremont provide an important case study to examine the resilience of ancient farmers to climatic downturns, for they lived at the far northern margin of intensive maize agriculture in the American West, where the constraints on maize production are made abundantly clear. Using a tree-ring and simulation-based reconstruction of average annual precipitation and maize growing degree days, along with cost-distance to perennial streams, we model spatial variability in Fremont site density in the eastern Great Basin. The results of our analysis have implications for defining the ecological envelope in which farming is a viable strategy across this arid region and can be used to predict where and why maize farming strategies might evolve and eventually collapse as climate changes over time.
keywords:
  - Ideal Free Distribution
  - Great Basin
  - Paleoclimate Reconstruction
bibliography: bibliography.bib
linenumbers: false
watermark: false
format: 
  simple-pdf: default
execute: 
  echo: false
  error: false
  warning: false
---

@@

![
On the left is an overview map showing the project area with modern satellite imagery. Dark green colors represent high elevation, high precipitation areas. The large beige area in the northwest is the Bonneville Basin. What remains of the Great Salt Lake can be seen just west of Salt Lake City. For visualization purposes, the map on the right shows the relative density of archaeological sites (see the section on site data below for details on how we calculate relative density). Please note that although the map appears to show many empty watersheds, most do in fact contain archaeological sites, just at extremely low densities.
](../figures/overview.jpg){#fig-overview fig-align="center" width="6in"}

@@

![
Linear responses of average water-year precipitation (mm), average growing-season maize gdd (C), and cost-distance to streams (hours) to changes in elevation (m). See methods for how these values were calculated and results for more details.
](../figures/elevation-everything.jpg){#fig-elevation fig-align="center" width="4in"}

@@

Many social and ecological variables may be relevant to defining a general measure of $S_i$, but here we are focusing on ecological determinants of intrinsic habitat quality, $Q_i$, that are specific to maize farmers. Our reasoning here is fairly straightforward. If we assume that the distribution of Fremont populations across habitats is at equilibrium, then we can combine this concept of maize-specific suitability with the input matching rule to reconstruct the ranking of habitats on the basis of ecologically-relevant parameters. In other words, it follows from their being at equilibrium that any observed differences in population size, $N_i$, must be the result of differences in $Q_i$. So, if we have some proxy for $N_i$, like the distribution of Fremont sites across habitats, we can model that value as a function of ecological covariates, $X_i$, then use the resulting model to reconstruct $Q_i \sim f(X_i)$, giving us the maize niche for Fremont farmers, both in geographic and ecological space.

@@

@fig-overview shows the relative density of Fremont sites across watersheds. The *relative* density refers to the density of feature-weighted sites ($D_i = N_i/area_i$) divided by the maximum density ($max\;D$) across all watersheds, thus scaling the density estimates to the unit interval [0,1]. Using the relative density is just a visual tool to help avoid any implication that we have an independent estimate of the absolute number of Fremont sites in the area, and not just an estimate based on a thinned sample.

@@

![
Distribution of covariates across watersheds. These include maize growing degree days (GDD), annual precipitation (precipitation), and cost-distance to streams (Streams).
](../figures/covariates.jpg){#fig-covariates fig-align="center" width="6in"}

@@

The response variable is a count $N$ of sites per watershed $i$, so it should arise as the result of a Poisson process. Given the trade-offs outlined above, we also expect it to exhibit a non-linear response to precipitation, GDD, and cost-distance to streams, so we fit a generalized additive model (GAM) with a log-link to the data using the R package mgcv [@wood2004]. Although we expect the outcome to be Poisson distributed, we use a negative binomial distribution here, as this includes a parameter, $r$, that can account for potential dispersion without giving up the inferential benefits of maximum likelihood.
$$
\begin{aligned}
N_i \sim& \;NB\,(\lambda, r)\\
E\,(N_i) =& \;\lambda_i\\
log\, (\lambda_i) =& \;log\, (area_i) + s(precipitation_i) + streams_i + gdd_i + protected_i
\end{aligned}
$$

@@

![
Marginal response plots. Each plot shows the response of site counts to changes in a target covariate while holding all other variables at their mean.
](../figures/marginal_response.jpg){#fig-responses fig-align="center" width="5in"}

@@

Our results indicate that Fremont maize farmers generally preferred warmer watersheds with longer growing seasons, moderate levels of precipitation (in the range of 400-600 mm), and greater access to perennial streams, as shown by the marginal response plots in Fig. 3. While site counts exhibit a positive linear response to maize GDD in our model, this should not be expected to continue indefinitely for the obvious reason that maize has an upper threshold temperature at which point it no longer grows. Plus, increased temperatures trade-off with water availability, with warmer conditions being better for plant growth but at the same time increasing water demand on the plant to keep up with growth [@ramankutty2002]. The linear relationship between site counts and maize GDD is, thus, relative to the observed distribution of that variable within the study area and should not be used to generalize outside of that distribution.

@@

Provided that the trade-off between precipitation and temperature is driven largely by elevation in this region, it would seem likely that the western Fremont chose site locations at elevations that maximized agricultural suitability, as evidenced by the estimated distribution of sites across watersheds (see Fig. 4), though we caution that watersheds are coarse grained units of analysis. Given the topography of the study area, this trade-off would also suggest that areas suitable for maize agriculture take the form of a thin band around the lower slopes of mountain ranges (or lower canyons in the Uintas). Such a band would be akin to a Goldilocks zone for maize agriculture (Yaworsky et al, in press), a place where the optima for GDD and precipitation overlap.

We should take care not to over-interpret this idea, however, for it is an area of overlap for continuous ecological gradients, not a region demarcated by anything like a perfect line. It should also be emphasized that what matters most for maize agriculture is not necessarily where precipitation falls, but where it accumulates once it enters the stream flow network. Of course, that will largely be a function of elevation in this region, or changes in elevation, so it will still be in proximity to the Goldilocks zone, though perhaps not perfectly coincident with it. At any rate, given these considerations, it would perhaps be more accurate to characterize the trade-off confronting the Fremont as one between what we might call water availability (including general precipitation across the stream flow network, water runoff, proximity to perennial surficial sources, and irrigation potential, among other things) and temperature (including, but not limited to, the length of the growing season and the number of frost-free days).

@@

![
The map on the left shows the relative density of feature-weighted site counts as estimated by the model, with lighter colors representing larger relative densities, darker colors representing smaller relative densities. The map on the right shows which watersheds are in the rain-fed maize farming niche for at least half of the Fremont sequence. The light green color indicates those that are in the niche.
](../figures/threshold_map.jpg){#fig-thresholds fig-align="center" width="6in"}

@@

But setting aside those methodological issues, some much more interesting explanations may be offered, at least from the perspective of theory. In particular, the spatial covariance structure in our model may be picking up on the structure of the stream flow network, specifically the accumulation of water run-off as a function of slope. This would suggest that if there are more people in one watershed, there should be more more people in the downstream watershed, too, at least relative to other watersheds with similar precipitation and GDD values. In the language of the IFD model, the suitability of the watershed habitat should propagate through the stream flow network. Exploring that intuition in a more systematic way, however, would require much more careful consideration of stream flow. Unfortunately, that is well beyond the scope of the current paper.

@@

![
Geographic distribution of Fremont sites across watersheds. The left panel shows the relative density derived from observed site counts, and the right panel shows the relative density from the estimated site counts.
](../figures/model-map.jpg){#fig-model-map fig-align="center" width="6in"}
